---
title: "Formules mathématiques"
output:
  pdf_document: 
    toc: true
    toc_depth: 2
    number_sections: true
  html_document: 
    toc: true
    toc_depth: 2
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:\\DataHEPL\\repos\\B2\\RMarkDownTest")
getwd()
```

\pagebreak
# Statistique descriptive à une dimension en R

```{r}
plot(cars)
```

## Titre 2
```{r, include=FALSE, cache=FALSE}
#lire ici le fichier Somme.R qui est dans le dossier défini au dessus
knitr::read_chunk('Somme.R')
```
**Initialisation-de-variables**\
J'essaie ici d'initialiser mes nombres
```{r, Initialisation-de-variables}
```
**Somme de deux nombre**\
J'essaie ici de calculer la *somme* de deux nombres.
```{r, Somme-de-nombres}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
